Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-12 article/article.tex
results

Wang et al. \cite{wa:2003betw} used GNB and Support Vector Machine (SVM) as cross-subject classifiers in a sentence versus picture study, in a similar context as our conducted study. When using the averaging technique (averaging all voxels in an ROI into a supervoxel) and normalization, GNB yielded a predictive performance of 74.3\%, while SVM 75.3\%.

>>>>

To compare our results with other related studies, Wang et al. \cite{wa:2003betw} used GNB and Support Vector Machine (SVM) as cross-subject classifiers in a sentence versus picture study. When using the averaging technique (averaging all voxels in an ROI into a supervoxel) and normalization, GNB yielded a predictive performance of 74.3\%, and SVM 75.3\%. Our results denote a higher performance, where using normalization GNB yielded a performance of 76.67\% and LSVM 76.88\%.
